Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-05-13 Neurophotonics/Submitted files/manuscript_revision.tex
commit after submission of revised manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. To this end, we have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from streaming of raw images up to stitching of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, whole brain imaging, data management, software management, imaging pipeline, high-throughput imaging}

@@

		\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:excitation} (A) Schematic of the light path. The galvo scanners are mounted above periscopes. LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter. Green dotted: detection path. (B) Oblique view of the microscope. A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages. A second breadboard is used for the camera.} 
   \end{figure}

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The focal lengths of the doublets making up the telescope have been chosen for space considerations and to achieve a $1/e^2$ beam radius of 0.73mm at the back focal plane resulting in an effective NA of 0.025 (see also section \ref{sec:characterisation}). The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. Additionally each line in the specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame2.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:frame2} Schematic of sample mounting and motion. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light-sheet and the detection focal plane overlap. (B) The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D). (E) Mounting of a clarified fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.} 
   \end{figure}

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $n \approx 1.45$\cite{Costantini}. To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame3.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of nanometric beads and fits to Gaussian curves. (B) FWHM of the Gaussian fits with confocal slit width. Each data point is the average of 10 bead profiles. (C) Signal to noise ratio (SNR) as a function of slit width.} 
\end{figure}

@@

\subsection{General design}
The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US). Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, stringent software design is a primary concern. The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance. This means, the apparatus should be able to deal with many independent hardware components and with several data streams (see below). Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time. Any kind of hardware failure, from timing delays to complete system crash, must be automatically handled to avoid loss of data.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame4.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colours.} 
   \end{figure}

@@

Synchronization of the camera rolling shutter to the scanning of the light sheet was achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers. The HSYNC signal from the camera was used which provided true-type-logic (TTL) pulse every time the rolling shutter stepped from one line to the next one. This trigger signal was used as a clock by the DAQ board so that the line producing the light sheet moved step by step with the rolling shutter. The same HSYNC signal was also used to trigger the DAQ digital signal sent to the laser modulator. Since at each position of the scanning line the modulator should go trough at least two states (vertical and horizontal polarization), HSYNC was used as a trigger while the the much faster internal clock of the DAQ board served as clock.

\subsection{Software organisation}
Each hardware component in the LSFM was managed through its own software component (see supplementary information \ref{sec:murmex}). Since the galvo scanners and the electro-optical modulator were not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sent analog and digital waveforms to an additional intermediate component responsible for DAQ board management. Beyond hardware-related software, two additional software components, the Stack and Tomo components orchestrated the operation of the entire system.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{DataFlow.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:DataFlow} Scheme of the data flow. (A) Data streaming on the microscope. SSD: solid-state disk, RAID: redundant array of independent disks. Colours indicate the time-criticality (red: higher to green: lower) of each data stream. (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up. NAS: network-attached storage} 
   \end{figure}

@@

The camera flushed the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB. Although this was already a large and expensive system for the current SSD technology, it was much smaller than the size of the raw datasets produced in each tomography. We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable. The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space. The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre). The data flow scheme is summarized in Fig. \ref{fig:DataFlow}.

While transferring data from the SSDs to the NAS, we perform on-the-fly conversion of files generated during sample acquisitions to a losslessly compressed multi-page TIFF format. Our conversion module leveraged the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library. The module read a single \textit{.cxd} 3D image and wrote it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file. Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format was read slice by slice to minimize memory requirements. The conversion module ran concurrently with the microscope controlling software and was synchronized to convert stack files as soon as they are completed. The module provided options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements. Usually we downsampled the image in the XY plane by a factor 2 and left the Z sampling unaltered. This downsampling, in combination with the lossless compression offered by the TIFF format, reduced data size by about one order of magnitude. Thus the parallelepiped volume containing the whole mouse brain took up about 2-3 TB of disk space.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{data_panel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective. (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$. (C,D,E) High resolution insert, of the stack corresponding to red boxes in B. Scale bar = $100 \micro m$. Modified with permission from \cite{Costantini}.} 
   \end{figure}

Some representative data produced by our microscope are reported in Fig. \ref{fig:LSMdata}. With the apparatus described in this paper, whole mouse brains could be imaged in their entirety (Fig. \ref{fig:LSMdata},A), maintaining a high quality of the image also when going deep inside the specimen (Figs. \ref{fig:LSMdata},B). The resolution and contrast of the images allowed to distinguish axonal tracts (Fig. \ref{fig:LSMdata},C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labelled. GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig. \ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain (Fig. \ref{fig:LSMdata},E). Such whole-brain datasets can be used to localize cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.

@@

%clearing
The mouse brains imaged in our microscope are intrinsically opaque and need to be clarified before imaging. A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for the high-throughput imaging of large samples that we aim for, the protocol, however, is also fast, easy and cheap. We therefore developed a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or portions of human tissue.

@@

Additionally another problem inherent to light-sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light sheet and the detection FOV when large samples are imaged at depths. Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012}. The prospect of high quality images is especially essential for high through-put imaging methods for whole-brain 3D reconstructions because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}. The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data. We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path. The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole-brain reconstructions will be considered in the future.

@@

\bibitem{Costantini} I. Costantini, J.-P. Ghobril, A. P. Di Giovanna, A. L. Allegra Mascaro, L. Silvestri, M. C. M\"{u}llenbroich, L. Onofri, V. Conti, F. Vanzi, L. Sacconi, R. Guerrini, H. Markram, G. Iannello, and F. S. Pavone, \emph{submitted}.

@@

%\bibitem{Kaufmann2012} A. Kaufmann, M. Mickoleit, M. Weber and J. Huisken, ``Multilayer mounting enables long-term imaging of zebrafish development in a light-sheet microscope," \emph{Development} \textbf{139}(17), 3242-3247 (2012).
%
%\bibitem{Pitrone2013} P. Pitrone, J. Schindelin, L. Stuyvenberg, S. Preibisch, M. Weber, K. W. Eliceiri, J. Huisken and P. Tomancak, ``OpenSPIM-an open access platform for light-sheet microscopy," \emph{arXiv} reprint arXiv:1302.1987, 3242-3247 (2013).
%
%\bibitem{Olarte2012} O. E. Olarte, J. Licea-Rodriguez, J. A. Palero, E. J. Gualda, D. Artigas, J. Mayer and P. Loza-Alvarez, ``Image formation by linear and nonlinear digital scanned light-sheet fluorescence microscopy with Gaussian and Bessel beam profiles," \emph{Biomedical optics express} \textbf{3}(7), 1492-1505 (2012).

@@

%\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel3.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment} (A) Basic geometrical optics of a double-sided illumination light-sheet microscope. AD: achromatic doublet, PBS: polarising beam splitter, red: objective back focal planes and conjugated telecentric planes, green: image planes, blue: 4f telecentric lens system, black: alignment irises. (B) Alignment mirror with drilled hole for light transmission, mount for tip adjustment and adaptor for the Teflon tube. (C) With lateral movement the alignment mirror can be placed such that light is transmitted into the opposing excitation arm. (D) The alignment mirror can be rotated to precisely reflect by $90\degree$.} 
   \end{figure}

@@

Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber. The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Fig. \ref{fig:alignment},B). Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror. With this ``sample mirror" three different position can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig. \ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Fig. \ref{fig:alignment},D).

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{Panel4.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:alignment2} (A) Working principle of a microscope objective (left): a collimated input beam is converted into a spherical wavefront. Right: inverted light path, a focal spot in the back aperture creates a collimated output. (B) Recursive placement of lenses using the sample mirror in back-reflection mode, (C) in transmission mode and (D) in reflection mode.} 
   \end{figure}

@@

Mouse brains were processed using a modified CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}. Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS. We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at $4 \degree$ C for 3 days. Afterwards, we degassed the samples and increased their temperature to $37 \degree$ C to initiate polymerization. The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at $37 \degree $ C through gentle shaking. To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber. The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at $37 \degree$ C for several days. After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at $37 \degree$ C for 2 days to remove the clearing solution. As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at $37 \degree$ C while gently shaking. The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.

\subsection{Murmex}
\label{sec:murmex}
	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{murmex.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
   \end{figure}

To operate the software efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used. This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardized programming scheme.

Murmex creates distributed finite state machines, design patterns in which one component proceeds from a particular state to another based on the message it receives either from itself or from other components. For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middle-ware, however, these layers of abstraction are mostly hidden from the developers. %The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network. 
Buffered, asynchronous and reliable communication between several software components is established by routing of messages by the broker to the specific software component pinpointed by its ID. %The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
Murmex has twelve pre-defined states (eg, Initialise, Configure, Start, Stop, Proceed, Update) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard application. An example of a standard implementation of the Murmex state machine for the camera is shown in Fig. \ref{fig:murmex}. Each Murmex component streams information about its current status to its 'observers' which are other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design a large and complex network of different components, running on various computers connected through a local connection or the internet while maintaining precise timing and synchronisation. %A special component, named ServiceManager (also based on Murmex), which must be running on each computer, allows to start executables remotely in user-defined compositions of components. This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but operated from one computer.

@@

\end{spacing}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. To this end, we have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from streaming of raw images up to stitching of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterisation and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, selective plane illumination microscopy, whole brain imaging, data management, software management, high-throughput imaging}

@@

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The focal lengths of the doublets making up the telescope have been chosen for space considerations and to achieve a $1/e^2$ beam radius of 0.73mm at the back focal plane resulting in an effective NA of 0.025 (see also section \ref{sec:characterisation}). The galvos are in planes conjugated with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. Additionally each line in the specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $n \approx 1.45$\cite{Costantini}. To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed. A motorised x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

@@

@@

\subsection{General design}
The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software written in the LabVIEW language (National Instruments, Austin, US). Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronisation, stringent software design is a primary concern. The overall architecture of the software and its practical implementation were chosen to satisfy two main principles; firstly, operation in a distributed environment and secondly, robustness and ease of maintenance. This means, the apparatus should be able to deal with many independent hardware components and with several data streams (see below). Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time. Any kind of hardware failure, from timing delays to complete system crash, must be automatically handled to avoid loss of data.

@@

@@

Synchronisation of the camera rolling shutter to the scanning of the light sheet was achieved by letting the camera acquiring in free-run mode, and using a trigger output from the camera itself to time the generation of the waveforms sent to the galvo drivers. The HSYNC signal from the camera was used which provided true-type-logic (TTL) pulse every time the rolling shutter stepped from one line to the next one. This trigger signal was used as a clock by the DAQ board so that the line producing the light sheet moved step by step with the rolling shutter. The same HSYNC signal was also used to trigger the DAQ digital signal sent to the laser modulator. Since at each position of the scanning line the modulator should go trough at least two states (vertical and horizontal polarisation), HSYNC was used as a trigger signal while the the much faster internal clock of the DAQ board served as clock.

@@

@@

The camera flushed the data stream directly to a dedicated workstation with 12 solid-state drives (SSD) operating in RAID 0 configuration, resulting in a virtual drive of 10.9 TB. Although this was already a large and expensive system for the current SSD technology, it was much smaller than the size of the raw datasets produced in each tomography. We thus connected the workstation to a larger network area storage (NAS) via a 10 Gbit/s network copper cable. The NAS operates in a safer data modality (RAID 5) with 32.4 TB of useful disk space. The NAS is then connected by a dedicated 10 Gbit/s link provided by the Consortium GARR (the Public Institution managing research networks in Italy) to CINECA (the main Italian supercomputing centre). The data flow scheme is summarised in Fig. \ref{fig:DataFlow}.

While transferring data from the SSDs to the NAS, we perform on-the-fly conversion of files generated during sample acquisitions to a losslessly compressed multi-page TIFF format. Our conversion module leveraged the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library. The module read a single \textit{.cxd} 3D image and wrote it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file. Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format was read slice by slice to minimise memory requirements. The conversion module ran concurrently with the microscope controlling software and was synchronised to convert stack files as soon as they are completed. The module provided options to downsample the image or to save the input image at full or reduced resolution in order to adapt to storage requirements. Usually we downsampled the image in the XY plane by a factor 2 and left the Z sampling unaltered. This downsampling, in combination with the lossless compression offered by the TIFF format, reduced data size by about one order of magnitude. Thus the parallelepiped volume containing the whole mouse brain took up about 2-3 TB of disk space.

@@

Some representative data produced by our microscope are reported in Fig. \ref{fig:LSMdata}. With the apparatus described in this paper, whole mouse brains could be imaged in their entirety (Fig. \ref{fig:LSMdata},A), maintaining a high quality of the image also when going deep inside the specimen (Fig. \ref{fig:LSMdata},B). The resolution and contrast of the images allowed to clearly distinguish axonal tracts (Fig. \ref{fig:LSMdata},C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labelled. Lateral and axial intensity profiles through a fine axonal projection were used to estimate resolution in a brain data set in terms of the FWHM in the lateral and axial directions (Fig. \ref{fig:LSMdata},D). The lateral and axial FWHM were $1.7 \micro m$ and $8.5 \micro m$ respectively, in agreement with the measurements on fluorescent beads.  Whole-brain datasets as presented here can be used to localise cell distributions in 3D using automatic cell-detection software \cite{Frasconi2014}.

@@

%clearing
The mouse brains imaged in our microscope are intrinsically opaque and need to be clarified before imaging. A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridised, lipid-free form. Crucially for the high-throughput imaging of large samples that we aim for, the protocol, however, is also fast, easy and cheap. We therefore developed a versatile, simple, rapid and inexpensive clearing method described elsewhere\cite{Costantini} which in combination with CLARITY allows for the optical clearing of entire mouse brains or portions of human tissue.

@@

Additionally another problem inherent to light-sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light sheet and the detection FOV when large samples are imaged at depths. Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012}. The prospect of high quality images is especially essential for high through-put imaging methods for whole-brain 3D reconstructions because the size of data sets is so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}. The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data. We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path. The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole-brain reconstructions will be considered in the future.

@@

\bibitem{Costantini} I. Costantini, J.-P. Ghobril, A. P. Di Giovanna, A. L. Allegra Mascaro, L. Silvestri, M. C. M\"{u}llenbroich, L. Onofri, V. Conti, F. Vanzi, L. Sacconi, R. Guerrini, H. Markram, G. Iannello, and F. S. Pavone, ``A versatile clearing agent for multi-modal brain imaging," \emph{Sci. Rep.} \textbf{5}(9808), (2015).

@@

@@

@@

@@

Our microscope was aligned with two tools, a shear plate to qualitatively assess collimation and a small mirror that can be mounted inside the sample chamber. The 0.5in mirror was first pierced with a drill using a ceramic drill bit to produce a hole roughly in its centre of the approximately the same diameter as the excitation beam inside the sample chamber (Fig. \ref{fig:alignment},B). Using a compact single axis adjustable mirror mount (V50-AX, Newport) attached to the Teflon cylinder allows to to adjust the pitch of the reflection with the mount and the yaw with the rotation stage while at the same time providing a very space efficient mounting for the pierced 0.5in mirror. With this ``sample mirror" three different positions can be easily implemented, firstly, back reflection by hitting the reflective surface at $0\degree$, secondly, transmission by laterally displacing the mirror until the light passes through the drilled hole (Fig. \ref{fig:alignment},C), and thirdly, reflection of the light by $90\degree$ by precisely turning the mirror mount by $45\degree$ using the rotation stage (Fig. \ref{fig:alignment},D).

@@

Mouse brains were processed using a modified CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}. Adult mice (post-natal day 56) were anaesthetised with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS. We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at $4 \degree$ C for 3 days. Afterwards, we degassed the samples and increased their temperature to $37 \degree$ C to initiate polymerisation. The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at $37 \degree $ C through gentle shaking. To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber. The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at $37 \degree$ C for several days. After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at $37 \degree$ C for 2 days to remove the clearing solution. As a final step, murine brains were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at $37 \degree$ C while gently shaking. The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency. The experimental protocols involving animals were designed in accordance with the laws of the Italian Ministry of Health. All experimental protocols were approved by the Italian Ministry of Health.

\subsection{Murmex}
\label{sec:murmex}

To operate the software efficiently and synchronously on different machines, the \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex} software development kit was used. This kit integrates the object-oriented programming paradigm with a messaging system, and can be used to create communicating yet independent software modules within a standardised programming scheme.

Murmex creates distributed finite state machines, design patterns in which one component proceeds from a particular state to another based on the message it receives either from itself or from other components. For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middle-ware, however, these layers of abstraction are mostly hidden from the developers. 
Buffered, asynchronous and reliable communication between several software components is established by routing of messages by the broker to the specific software component pinpointed by its ID.
Murmex has twelve pre-defined states (eg, Initialise, Configure, Start, Stop, Proceed, Update) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard applications. An example of a standard implementation of the Murmex state machine for the camera is shown in Fig. \ref{fig:murmex}. Each Murmex component streams information about its current status to its 'observers' which are other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design a large and complex network of different components, running on various computers connected through a local connection or the internet while maintaining precise timing and synchronisation.

%\subsection{Software organisation}
Each hardware component in the LSFM was managed through its own software component (see supplementary information \ref{sec:murmex}). Since the galvo scanners and the electro-optical modulator were not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sent analog and digital waveforms to an additional intermediate component responsible for DAQ board management. Beyond hardware-related software, two additional software components, the Stack and Tomo components orchestrated the operation of the entire system.

@@

\newpage
\pagebreak
